---
title: "Exercise_3"
author: "Xinyuan Zhuang(12541600)"
date: "2025-06-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 1

### d)
Advantages:
   1)  It allows you to restore previous versions when errors occur.
   2) It is suitable for collaborative work; each person can complete their part and then merge the results.

Disadvantages:
   1) The commands are complex and prone to errors.
   2) When multiple people work on the same file, errors may occur if they modify the same part.
   

## Exercise 2

Here is the link to my GitHub repository:
https://github.com/z-x156/exeRcise-sheet-3


## Exercise 3

### a)
```{r, echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(readr)
library(dplyr)

pixar <- readr::read_csv("D:/Sose 25 Software R 2/Exercise 3/pixar_films.csv")

pixar_clean <- pixar %>% 
  filter(!is.na(film))

unique(pixar_clean$film_rating)
pixar_clean <- pixar_clean %>%
  mutate(film_rating_factor = factor(film_rating))

view(pixar_clean)

```
Because film_rating is a categorical variable, converting it into a factor allows it to be correctly handled in subsequent visualizations or statistical analyses.


### b)
```{r, echo=TRUE, message=FALSE, warning=FALSE}
str(pixar_clean)

pixar_clean <- pixar_clean %>%
  mutate(franchise = case_when(
    str_detect(film, "Toy Story") ~ "Toy Story",
    str_detect(film, "Cars") ~ "Cars",
    str_detect(film, "Finding") ~ "Finding",
    str_detect(film, "Incredibles") ~ "Incredibles",
    TRUE ~ "Other"
  ))

franchise_counts <- pixar_clean %>%
  group_by(franchise) %>%
  summarise(n = n())

library(ggplot2)

ggplot(franchise_counts, aes(x = reorder(franchise, n), y = n)) +
  geom_col(fill = "blue") +
  coord_flip() +
  labs(
    title = "Anzahl der Filme pro Franchise",
    x = "Franchise",
    y = "Filmanzahl"
  )

```
### c)
```{r, echo=TRUE, message=FALSE, warning=FALSE}
pixar <- read_csv("D:/Sose 25 Software R 2/Exercise 3/pixar_films.csv")
public_response <- read_csv("D:/Sose 25 Software R 2/Exercise 3/public_response.csv")

pixar_clean <- pixar %>%
  filter(!is.na(film))

merged_data <- left_join(pixar_clean, public_response, by = "film")

nrow(pixar_clean)
nrow(merged_data)

colnames(merged_data)

unmatched <- merged_data %>%
  filter(is.na(metacritic))

nrow(unmatched)
unmatched$film

```

We merged "pixar_films" with "public_response" using a left join on the film column. After the join, we checked for rows where variables like "metacritic" are missing.  
This indicates that some films did not have matching records in "public_response",  and they were possibly due to missing data or differences in film titles.


### d)
```{r, echo=TRUE, message=FALSE, warning=FALSE}
plot_data <- merged_data %>%
  filter(!is.na(metacritic), !is.na(critics_choice))

view(plot_data)
ggplot(plot_data, aes(x = metacritic, y = critics_choice)) +
  geom_point(color = "green", size = 2) +
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  labs(
    title = "Relationship between Metacritic and Critics' Choice",
    x = "Metacritic",
    y = "Critics' Choice"
  )
```





