---
title: "Exercise_3"
author: "Xinyuan Zhuang(12541600)"
date: "2025-06-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 1

### d)
Advantages:
   1)  It allows you to restore previous versions when errors occur.
   2) It is suitable for collaborative work; each person can complete their part and then merge the results.

Disadvantages:
   1) The commands are complex and prone to errors.
   2) When multiple people work on the same file, errors may occur if they modify the same part.
   

## Exercise 2

Here is the link to my GitHub repository:
https://github.com/z-x156/exeRcise-sheet-3


## Exercise 3

### a)
```{r, echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(readr)
library(dplyr)

pixar <- readr::read_csv("D:/Sose 25 Software R 2/Exercise 3/pixar_films.csv")

pixar_clean <- pixar %>% 
  filter(!is.na(film))

unique(pixar_clean$film_rating)
pixar_clean <- pixar_clean %>%
  mutate(film_rating_factor = factor(film_rating))

view(pixar_clean)

```
Because film_rating is a categorical variable, converting it into a factor allows it to be correctly handled in subsequent visualizations or statistical analyses.


### b)
```{r, echo=TRUE, message=FALSE, warning=FALSE}



```



